---
title: "1. Data Load and library integration"
author: "Cankun Wang, Faith Brennan"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(fig.width = 10, fig.height = 8)
library(Seurat)
library(ggplot2)
library(tidyverse)
library(devtools)
library(ggpubr)
library(Hmisc)
library(ggpubr)
library(ggrepel)
library(cowplot)
library(patchwork)
library(matrixStats)

```

# Load data and create objects for each dataset

Using R 3.6.3 and Seurat v3.2.0

R versions >4 will also provide the same data but some UMAP plots will appear rotated

```{r}
#Sample load  (n=6 libraries, three time points are sham, 7d and 28d)
A1.data <- Read10X(data.dir = "../Samples/1")
A1 <-
  CreateSeuratObject(
    A1.data,
    project = "00 d Control",
    assay = "RNA",
    min.cells = 3,
    min.features = 200
  )
A2.data <- Read10X(data.dir = "../Samples/2")
A2 <-
  CreateSeuratObject(
    A2.data,
    project = "00 d PLX5622",
    assay = "RNA",
    min.cells = 3,
    min.features = 200
  )
A3.data <- Read10X(data.dir = "../Samples/3")
A3 <-
  CreateSeuratObject(
    A3.data,
    project = "07 d Control",
    assay = "RNA",
    min.cells = 3,
    min.features = 200
  )
A4.data <- Read10X(data.dir = "../Samples/4")
A4 <-
  CreateSeuratObject(
    A4.data,
    project = "07 d PLX5622",
    assay = "RNA",
    min.cells = 3,
    min.features = 200
  )
A7.data <- Read10X(data.dir = "../Samples/7")
A7 <-
  CreateSeuratObject(
    A7.data,
    project = "28 d Control",
    assay = "RNA",
    min.cells = 3,
    min.features = 200
  )
A8.data <- Read10X(data.dir = "../Samples/8")
A8 <-
  CreateSeuratObject(
    A8.data,
    project = "28 d PLX5622",
    assay = "RNA",
    min.cells = 3,
    min.features = 200
  )



cord.grouped <-
  merge(
    A1,
    y = c(A2, A3, A4, A7, A8),
    add.cell.ids = c(
      "00 d Control",
      "00 d PLX5622",
      "07 d Control",
      "07 d PLX5622",
      "28 d Control",
      "28 d PLX5622"
    ),
    project = "all"
  )


```

# Data check

```{r}

head(colnames(cord.grouped))
tail(colnames(cord.grouped))
unique(sapply(X = strsplit(colnames(cord.grouped), split = "_"), FUN = "[", 1))
table(cord.grouped$orig.ident)

```

# Data integration

UMAP plots shown in Fig. 4B, D, E, F

```{r}

combinedgroup.list <- SplitObject(cord.grouped, split.by = "orig.ident")
combinedgroup.list <- lapply(X = combinedgroup.list, FUN = function(x) {
  x <- NormalizeData(x)
  x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = 2000)
})
combine.anchors <- FindIntegrationAnchors(object.list = combinedgroup.list, dims = 1:15)
combine.combined <- IntegrateData(anchorset = combine.anchors, dims = 1:15)
DefaultAssay(combine.combined) <- "integrated"
combine.combined <- ScaleData(combine.combined, verbose = FALSE)
combine.combined <- RunPCA(combine.combined, npcs = 30, verbose = FALSE)
combine.combined <- RunUMAP(combine.combined, reduction = "pca", dims = 1:15)
combine.combined <- FindNeighbors(combine.combined, reduction = "pca", dims = 1:15)
combine.combined <- FindClusters(combine.combined, resolution = 0.15)
DefaultAssay(combine.combined) <- "RNA"


```

# Find all markers and top DEGs in each cluster to assist with cluster identification

```{r}
seurat_markers <- FindAllMarkers(combine.combined)
write.csv(seurat_markers,"seurat_markers.csv")

#Data is in the .csv file “Seurat_markers”
clusterzero.de.markers <- FindMarkers(combine.combined, ident.1 = "0", ident.2 = NULL, only.pos = TRUE)
clusterone.de.markers <- FindMarkers(combine.combined, ident.1 = "1", ident.2 = NULL, only.pos = TRUE)
clustertwo.de.markers <- FindMarkers(combine.combined, ident.1 = "2", ident.2 = NULL, only.pos = TRUE)
clusterthree.de.markers <- FindMarkers(combine.combined, ident.1 = "3", ident.2 = NULL, only.pos = TRUE)
clusterfour.de.markers <- FindMarkers(combine.combined, ident.1 = "4", ident.2 = NULL, only.pos = TRUE)
clusterfive.de.markers <- FindMarkers(combine.combined, ident.1 = "5", ident.2 = NULL, only.pos = TRUE)
clustersix.de.markers <- FindMarkers(combine.combined, ident.1 = "6", ident.2 = NULL, only.pos = TRUE)
clusterseven.de.markers <- FindMarkers(combine.combined, ident.1 = "7", ident.2 = NULL, only.pos = TRUE)
clustereight.de.markers <- FindMarkers(combine.combined, ident.1 = "8", ident.2 = NULL, only.pos = TRUE)
clusternine.de.markers <- FindMarkers(combine.combined, ident.1 = "9", ident.2 = NULL, only.pos = TRUE)
clusterten.de.markers <- FindMarkers(combine.combined, ident.1 = "10", ident.2 = NULL, only.pos = TRUE)
clustereleven.de.markers <- FindMarkers(combine.combined, ident.1 = "11", ident.2 = NULL, only.pos = TRUE)
clustertwelve.de.markers <- FindMarkers(combine.combined, ident.1 = "12", ident.2 = NULL, only.pos = TRUE)
clusterthirteen.de.markers <- FindMarkers(combine.combined, ident.1 = "13", ident.2 = NULL, only.pos = TRUE)

#Use “head(clusterID.de.markers, n=50)” to preview de.markers for each cluster. 
#Export full de.marker list for each cluster
write.csv(clusterzero.de.markers, "microglia.de.markers")
write.csv(clusterone.de.markers, "MDM.de.markers")
write.csv(clustertwo.de.markers, "Endothelial.de.markers")
write.csv(clusterthree.de.markers, "Monocyte.de.markers")
write.csv(clusterfour.de.markers, "Astrocyte.de.markers")
write.csv(clusterfive.de.markers, "T cell.de.markers")
write.csv(clustersix.de.markers, "Ependymal.de.markers")
write.csv(clusterseven.de.markers, "B cell.de.markers")
write.csv(clustereight.de.markers, "Int prog.de.markers")
write.csv(clusternine.de.markers, "Neutrophil.de.markers")
write.csv(clusterten.de.markers, "Erythroid.de.markers")
write.csv(clustereleven.de.markers, "Oligo lineage.de.markers")
write.csv(clustertwelve.de.markers, "Pericyte.de.markers")
write.csv(clusterthirteen.de.markers, "Leptomeningeal.de.markers")

#FindMarker Files are combined into the excel file “Cluster.de.markers”. Genes for each cluster type are sorted by LogFC expression. The top 3 de genes for each cluster are highlighted in yellow and presented in the DotPlot in Fig. 4C.

```

# Rename clusters

Rename clusters if renaming is needed. For cluster isolation reserve the original labels.

```{r}
combine.combined <- RenameIdents(combine.combined, `0` = "Microglia")
combine.combined <- RenameIdents(combine.combined, `1` = "MDMs")
combine.combined <- RenameIdents(combine.combined, `2` = "Endothelial cells")
combine.combined <- RenameIdents(combine.combined, `3` = "Monocytes")
combine.combined <- RenameIdents(combine.combined, `4` = "Astrocytes") 
combine.combined <- RenameIdents(combine.combined, `5` = "T cells")
combine.combined <- RenameIdents(combine.combined, `6` = "Ependymal cells")
combine.combined <- RenameIdents(combine.combined, `7` = "B cells")
combine.combined <- RenameIdents(combine.combined, `8` = "Intermediate progenitors")
combine.combined <- RenameIdents(combine.combined, `9` = "Neutrophils")
combine.combined <- RenameIdents(combine.combined, `10` = "Erythroid cells")
combine.combined <- RenameIdents(combine.combined, `11` = "Oligodendrocyte lineage")
combine.combined <- RenameIdents(combine.combined, `12` = "Pericytes")
combine.combined <- RenameIdents(combine.combined, `13` = "Leptomeningeal cells")

Save(combine.combined, "combined.RData")

```

# Plot all cells

```{r, eval = T}
load("../data/Seurat output files/All cells/combined.RData.rda")
combine.combined <- combined.RData
DimPlot(combine.combined, reduction = "umap", group.by = "orig.ident", pt.size = 0.9)
DimPlot(combine.combined, reduction = "umap", group.by = "seurat_clusters", label = TRUE, pt.size = 0.9)
DimPlot(combine.combined, reduction = "umap", label = TRUE, pt.size = 0.9)


```

# Create a FeaturePlot showing de.markers (Sup. Fig. 7)

```{r, eval = T}
FeaturePlot(
  combine.combined,
  features = c(
    "P2ry12",
    "Gpnmb",
    "Ly6c1",
    "H2-Aa",
    "Atp1a2",
    "Ccl5",
    "Nnat",
    "Ly6d",
    "Stmn1",
    "S100a9",
    "Hba-a2",
    "Olig1",
    "Dcn",
    "Mgp"
  ),
  min.cutoff = "q9"
)
```

# Create a DotPlot showing de.markers

```{r, eval = T, fig.width=14, fig.height=6}
markers.to.plot <-
  c(
    "Gsn",
    "Igfbp6",
    "Mgp",
    "Vtn",
    "Dcn",
    "Apod",
    "Vcan",
    "Cspg5",
    "Olig1",
    "Alas2",
    "Hbb-bs",
    "Hba-a2",
    "Retnlg",
    "S100a8",
    "S100a9",
    "Top2a",
    "Hmgb2",
    "Stmn1",
    "Cd79b",
    "Cd79a",
    "Ly6d",
    "Mt3",
    "Nnat",
    "Dbi",
    "Nkg7",
    "Ms4a4b",
    "Ccl5",
    "Atp1b2",
    "Atp1a2",
    "Slc1a2",
    "H2-Ab1",
    "H2-Eb1",
    "H2-Aa",
    "Itm2a",
    "Cldn5",
    "Ly6c1",
    "Fabp5",
    "Spp1",
    "Gpnmb",
    "Tmem119",
    "Siglech",
    "P2ry12"
  )
DotPlot(
  combine.combined,
  features = rev(markers.to.plot),
  assay = "RNA",
  cols = c("blue", "orange"),
  dot.scale = 6
) + RotatedAxis()

```

#Show overall cluster data

```{r, eval = T}
cluster_cell_number <- (table(Idents(combine.combined)))
cluster_cell_number

cell_number_by_group<- table(Idents(combine.combined), combine.combined$orig.ident)
cell_number_by_group

cell_percent <- (prop.table(table(Idents(combine.combined), combine.combined$orig.ident), margin = 2))
cell_percent
#Files are combined into the file excel  “Cell numbers” and data is shown in Fig. 4D-H.
```

