---
title: "2. Microglia cluster analysis"
author: "Cankun Wang, Faith Brennan"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(fig.width = 10, fig.height = 8)
library(Seurat)
library(ggplot2)
library(tidyverse)
library(devtools)
library(ggpubr)
library(Hmisc)
library(ggpubr)
library(ggrepel)
library(cowplot)
library(patchwork)
library(matrixStats)

load("../data/Seurat output files/Microglia/this_micro_obj.RData.rda")
this_micro_obj <- this_micro_obj.RData 
load("../data/Seurat output files/All cells/combined.RData.rda")
combine.combined <- combined.RData
Idents(combine.combined) <- combine.combined$seurat_clusters

```

# Microglia cluster analysis (cluster 0 from combine.combined object)

```{r}

this_ct <- 0
this_micro_obj <- subset(combine.combined, idents = this_ct)
DefaultAssay(this_micro_obj) <- "RNA"
this_micro_obj <- NormalizeData(this_micro_obj)
this_micro_obj <- FindVariableFeatures(this_micro_obj)
this_micro_obj <- ScaleData(this_micro_obj)
this_micro_obj <- RunPCA(this_micro_obj, verbose = FALSE)
this_micro_obj <- FindNeighbors(this_micro_obj, dims = 1:50)
this_micro_obj <- FindClusters(this_micro_obj, resolution = 0.8)
this_micro_obj <- RunUMAP(this_micro_obj, reduction = "pca", dims = 1:50)
Idents(this_micro_obj) <- this_micro_obj$seurat_clusters
Save(this_micro_obj, "this_micro_obj.RData")

```

# Check top DEGs in each cluster to assist with cluster description

```{r}

clusterzero.de.markers <- FindMarkers(this_micro_obj, ident.1 = "0", ident.2 = NULL, only.pos = TRUE)
clusterone.de.markers <- FindMarkers(this_micro_obj, ident.1 = "1", ident.2 = NULL, only.pos = TRUE)
clustertwo.de.markers <- FindMarkers(this_micro_obj, ident.1 = "2", ident.2 = NULL, only.pos = TRUE)
clusterthree.de.markers <- FindMarkers(this_micro_obj, ident.1 = "3", ident.2 = NULL, only.pos = TRUE)
clusterfour.de.markers <- FindMarkers(this_micro_obj, ident.1 = "4", ident.2 = NULL, only.pos = TRUE)
clusterfive.de.markers <- FindMarkers(this_micro_obj, ident.1 = "5", ident.2 = NULL, only.pos = TRUE)
clustersix.de.markers <- FindMarkers(this_micro_obj, ident.1 = "6", ident.2 = NULL, only.pos = TRUE)
clusterseven.de.markers <- FindMarkers(this_micro_obj, ident.1 = "7", ident.2 = NULL, only.pos = TRUE)
clustereight.de.markers <- FindMarkers(this_micro_obj, ident.1 = "8", ident.2 = NULL, only.pos = TRUE)
clusternine.de.markers <- FindMarkers(this_micro_obj, ident.1 = "9", ident.2 = NULL, only.pos = TRUE)
clusterten.de.markers <- FindMarkers(this_micro_obj, ident.1 = "10", ident.2 = NULL, only.pos = TRUE)

#Use “head(clusterID.de.markers, n=50)” to preview de.markers for each microglia cluster. 
#Export full de.marker list for each cluster
write.csv(clusterzero.de.markers, "0.de.markers")
write.csv(clusterone.de.markers, "1.de.markers")
write.csv(clustertwo.de.markers, "2.de.markers")
write.csv(clusterthree.de.markers, "3.de.markers")
write.csv(clusterfour.de.markers, "4.de.markers")
write.csv(clusterfive.de.markers, "5.de.markers")
write.csv(clustersix.de.markers, "6.de.markers")
write.csv(clusterseven.de.markers, "7.de.markers")
write.csv(clustereight.de.markers, "8.de.markers")
write.csv(clusternine.de.markers, "9.de.markers")
write.csv(clusterten.de.markers, "10.de.markers")

#.csv files are combined into the excel file “Microglia clusters”

subcluster.averages <- AverageExpression(this_micro_obj, assays = "RNA", "subcluster.averages")
write.csv(subcluster.averages, "Microglia subcluster gene avgs")

#Data is in the far right tab of the excel file “Microglia clusters” 

```

# Rename clusters

```{r, eval = T}
Idents(this_micro_obj) <- this_micro_obj$seurat_clusters
this_micro_obj <- RenameIdents(this_micro_obj, `4` = "Homeostatic 1") 
this_micro_obj <- RenameIdents(this_micro_obj, `8` = "Homeostatic 2")
this_micro_obj <- RenameIdents(this_micro_obj, `1` = "Proliferating")
this_micro_obj <- RenameIdents(this_micro_obj, `5` = "Non-lipid phagocytosing")
this_micro_obj <- RenameIdents(this_micro_obj, `0` = "Lipid processing 1")
this_micro_obj <- RenameIdents(this_micro_obj, `2` = "Patrolling")
this_micro_obj <- RenameIdents(this_micro_obj, `6` = "Lipid processing 2")
this_micro_obj <- RenameIdents(this_micro_obj, `9` = "Antigen processing")
this_micro_obj <- RenameIdents(this_micro_obj, `3` = "Iron processing")
this_micro_obj <- RenameIdents(this_micro_obj, `7` = "Interferon production")
this_micro_obj <- RenameIdents(this_micro_obj, `10` = "Antigen binding")

```


# Plot all cells

```{r, eval = T}
DimPlot(this_micro_obj, label = TRUE, pt.size = 1)
DimPlot(this_micro_obj, reduction = "umap", split.by = "orig.ident", ncol = 2, pt.size = 0.7)

```

# Create a FeaturePlot showing de.markers (Sup. Fig. 8)

```{r, eval = T}
FeaturePlot(this_micro_obj, features = c("P2ry12", "Cx3cr1", "Fau", "Lgals1", "Clec7a", "Cst3", "Ctsd", "Lyz2", "Fth1", "Ifit3", "H2-Ab1"), min.cutoff = "q9")
```

# Create a DotPlot showing two of the de.markers for each cluster 

```{r, eval = T, fig.width=10, fig.height=5}
markers.to.plot <-
  c(
    "H2-Aa",
    "H2-Ab1",
    "Ifit1",
    "Ifit3",
    "Ftl1",
    "Fth1",
    "Cd93",
    "Lyz2",
    "Ctsz",
    "Ctsd",
    "Selplg",
    "Cst3",
    "Lpl",
    "Clec7a",
    "Pf4",
    "Lgals1",
    "Uba52",
    "Fau",
    "Csf1r",
    "Cx3cr1",
    "Ier5",
    "P2ry12"
  )

DotPlot(
  this_micro_obj,
  features = rev(markers.to.plot),
  assay = "RNA",
  cols = c("blue", "orange"),
  dot.scale = 6
) + RotatedAxis()

```

# Show microglia cluster data

```{r, eval = T}

microglia_cluster_cell_number <- (table(Idents(this_micro_obj)))
#write.csv(microglia_cluster_cell_number, "Microglia cluster cell number")
microglia_cluster_cell_number

Microglia_cell_number_by_group<- table(Idents(this_micro_obj), this_micro_obj$orig.ident)
#write.csv(Microglia_cell_number_by_group, "Microglia cell number_by group")
Microglia_cell_number_by_group

microglia_cell_percent <- (prop.table(table(Idents(this_micro_obj), this_micro_obj$orig.ident), margin = 2))
#write.csv(microglia_cell_percent, "Microglia cell percentages")
microglia_cell_percent

#Files are combined into the file excel  “Microglia cell numbers” and data is shown in Fig. 5A-F
```

# Violin plots for Fig. 5G-M

```{r, eval = T}
VlnPlot(
  combine.combined,
  features = c("P2ry12", "Fau", "Lgals1", "Clec7a", "Cst3", "Ctsd", "Fth1"),
  idents = "0",
  group.by  = "orig.ident",
  pt.size = 1,
  assay = "RNA"
)

```

# Statistical analysis for Fig. 5G-M

```{r}
microglia_7dvs0d <-
  FindMarkers(
    object = combine.combined,
    ident.1 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "07 d Control", ]),
      idents = "0"
    ),
    ident.2 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "00 d Control", ]),
      idents = "0"
    ),
    min.pct = 0.1,
    logfc.threshold = 0.176,
    assay = "RNA",
    only.pos = FALSE
  )
write.csv(microglia_7dvs0d, "microglia 7d vs 0d")

```

# Volcano plots for Fig. 5N, O

```{r}
microglia_7dvs0d <-
  FindMarkers(
    object = combine.combined,
    ident.1 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "07 d Control", ]),
      idents = "0"
    ),
    ident.2 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "00 d Control", ]),
      idents = "0"
    ),
    min.pct = 0.1,
    logfc.threshold = 0.176,
    assay = "RNA",
    only.pos = FALSE
  )
write.csv(microglia_7dvs0d, "microglia 7d vs 0d")
microglia_28dvs0d <-
  FindMarkers(
    object = combine.combined,
    ident.1 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "28 d Control", ]),
      idents = "0"
    ),
    ident.2 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "00 d Control", ]),
      idents = "0"
    ),
    min.pct = 0.1,
    logfc.threshold = 0.176,
    assay = "RNA",
    only.pos = FALSE
  )
write.csv(microglia_28dvs0d, "microglia 28d vs 0d")

```

