---
title: "5. Endothelial cluster analysis"
author: "Cankun Wang, Faith Brennan"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(fig.width = 10, fig.height = 8)
library(Seurat)
library(ggplot2)
library(tidyverse)
library(devtools)
library(ggpubr)
library(Hmisc)
library(ggpubr)
library(ggrepel)
library(cowplot)
library(patchwork)
library(matrixStats)

load("../data/Seurat output files/Endothelial cells/this_endo.RData.rda")
this_endo_obj <- this_endo.RData 
load("../data/Seurat output files/All cells/combined.RData.rda")
combine.combined <- combined.RData
Idents(combine.combined) <- combine.combined$seurat_clusters
```


```{r}
this_ct <- 2
this_endo_obj <- subset(combine.combined, idents = this_ct)
DefaultAssay(this_endo_obj) <- "RNA"
this_endo_obj <- NormalizeData(this_endo_obj)
this_endo_obj <- FindVariableFeatures(this_endo_obj)
this_endo_obj <- ScaleData(this_endo_obj)
this_endo_obj <- RunPCA(this_endo_obj, verbose = FALSE)
this_endo_obj <- FindNeighbors(this_endo_obj, dims = 1:20)
this_endo_obj <- FindClusters(this_endo_obj, resolution = 0.2)
this_endo_obj <- RunUMAP(this_endo_obj, reduction = "pca", dims = 1:20)
Idents(this_endo_obj) <- this_endo_obj$seurat_clusters
Save(combine.combined, "combined.RData")
Save(this_endo_obj, "this_endo.RData")

```


# Check top DEGs in each cluster to assist with endothelial cluster description

```{r}
clusterzero.de.markers <- FindMarkers(this_endo_obj, ident.1 = "0", ident.2 = NULL, only.pos = TRUE)
clusterone.de.markers <- FindMarkers(this_endo_obj, ident.1 = "1", ident.2 = NULL, only.pos = TRUE)
clustertwo.de.markers <- FindMarkers(this_endo_obj, ident.1 = "2", ident.2 = NULL, only.pos = TRUE)
clusterthree.de.markers <- FindMarkers(this_endo_obj, ident.1 = "3", ident.2 = NULL, only.pos = TRUE)

#Use “head(clusterID.de.markers, n=50)” to preview de.markers for each endothelial cluster. 
#Export full de.marker list for each cluster

write.csv(clusterzero.de.markers, "0.de.markers")
write.csv(clusterone.de.markers, "1.de.markers")
write.csv(clustertwo.de.markers, "2.de.markers")
write.csv(clusterthree.de.markers, "3.de.markers")

#.csv files are combined into the excel file “Endothelial clusters”

subcluster.averages <- AverageExpression(this_endo_obj, assays = "RNA", "subcluster.averages")
write.csv(subcluster.averages, "Endothelial subcluster gene avgs")

```


# Rename clusters

```{r, eval=T}
Idents(this_endo_obj) <- this_endo_obj$seurat_clusters
this_endo_obj <- RenameIdents(this_endo_obj, `0` = "Homeostatic") 
this_endo_obj <- RenameIdents(this_endo_obj, `1` = "Differentiating")
this_endo_obj <- RenameIdents(this_endo_obj, `3` = "Neovascularizing") 
this_endo_obj <- RenameIdents(this_endo_obj, `2` = "Perivascular macrophages") 

```

# Plot all cells

```{r, eval = T}

DimPlot(this_endo_obj, label = TRUE)
DimPlot(this_endo_obj, reduction = "umap", split.by = "orig.ident", ncol = 2)

```

# Create a DotPlot showing five of the de.markers for each cluster, showin in Sup. Fig. 11C


```{r, eval = T, fig.width=8, fig.height=4}
markers.to.plot <- c("Cd53", "Fcer1g", "Mpeg1", "Ly86", "Csf1r", "Rgs4", "Atp13a5", "Kcnj8", "Vtn", "Pdgfrb", "Cox14", "Fkbp4", "Ly6a", "Pltp", "Ly6c1", "Abcb1a", "App", "Afap1l1", "Mmrn2", "Cldn5")

DotPlot(this_endo_obj, features = rev(markers.to.plot), assay = "RNA", cols = c("blue", "orange"), dot.scale = 6) + RotatedAxis()

```

# Show Endothelial cell cluster data

```{r, eval = T}
Endothelial_cluster_cell_number <- (table(Idents(this_endo_obj)))
#write.csv(Endothelial_cluster_cell_number, "Endothelial cluster cell number")
Endothelial_cluster_cell_number

Endothelial_cell_number_by_group<- table(Idents(this_endo_obj), this_endo_obj$orig.ident)
#write.csv(Endothelial_cell_number_by_group, "Endothelial_cluster no._by group")
Endothelial_cell_number_by_group

Endothelial_cell_percent <- (prop.table(table(Idents(this_endo_obj), this_endo_obj$orig.ident), margin = 2))
#write.csv(Endothelial_cell_percent, "Endothelial cell percentages")
Endothelial_cell_percent

#Files are combined into the file excel  “Endothelial cell numbers” and data is shown in Sup. Fig. 11

```

# Violin plots for Sup. Fig. 11H, I, K, L

```{r, eval = T}
VlnPlot(combine.combined, features = c("Fth1", "Apoe", "Ubb", "Sox18"), idents = "2", group.by = "orig.ident", pt.size = 1, assay = "RNA")
```

# Statistical analysis for Sup. Fig. 11H, I, K, L

```{r}

FindMarkers(this_endo_obj, ident.1 = "Group 1", ident.2 = "Group 2", group.by = "orig.ident", features = c("gene name"), logfc.threshold = 0.001, test.use = "wilcox")

```

# Analysis for Volcano plot and heatmaps in Sup. Fig. 11

```{r}

Endo_7dvs0d <-
  FindMarkers(
    object = combine.combined,
    ident.1 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "07 d Control", ]),
      idents = "2"
    ),
    ident.2 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "00 d Control", ]),
      idents = "2"
    ),
    min.pct = 0.1,
    logfc.threshold = 0.176,
    assay = "RNA",
    only.pos = FALSE
  )
write.csv(Endo_7dvs0d, "Endothelial 7d vs 0d")

Endo_28dvs0d <-
  FindMarkers(
    object = combine.combined,
    ident.1 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "28 d Control", ]),
      idents = "2"
    ),
    ident.2 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "00 d Control", ]),
      idents = "2"
    ),
    min.pct = 0.1,
    logfc.threshold = 0.176,
    assay = "RNA",
    only.pos = FALSE
  )
write.csv(Endo_28dvs0d, "Endothelial 28d vs 0d")

Endo_7dplxvs7dveh <-
  FindMarkers(
    object = combine.combined,
    ident.1 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "07 d PLX5622", ]),
      idents = "2"
    ),
    ident.2 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "07 d Control", ]),
      idents = "2"
    ),
    min.pct = 0.1,
    logfc.threshold = 0.176,
    assay = "RNA",
    only.pos = FALSE
  )
write.csv(Endo_7dplxvs7dveh, "Endothelial 7dplx vs 7dveh")

Endo_28dplxvs28dveh <-
  FindMarkers(
    object = combine.combined,
    ident.1 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "28 d PLX5622", ]),
      idents = "2"
    ),
    ident.2 = WhichCells(
      combine.combined,
      cells = rownames(combine.combined@meta.data[combine.combined@meta.data$orig.ident ==
                                                    "28 d Control", ]),
      idents = "2"
    ),
    min.pct = 0.1,
    logfc.threshold = 0.176,
    assay = "RNA",
    only.pos = FALSE
  )
write.csv(Endo_28dplxvs28dveh, "Endothelial 28dplx vs 28dveh")

```


# Introduction of bootstrap

We use the "boot" R package to perform bootstrap analysis. The R package boot allows a user to easily generate bootstrap samples (10000) of virtually any statistic that they can calculate in R. We perform bootstrap analysis for the mixture of cell types from six samples.

Four outputs will be generated including:

* Variance of bootstrap resamples (needed by bootstrap using bca bootstrap method). Smaller variance indicates better consistency among the resamples.

* 95% Confidence Intervals (CIs) used to test the statistical confidence of the bootstrap results. 95% probability can be ensured that the estimated statistic falls within the CI. CIs are calculated by normal approximation (norm), basic bootstrap (basic), bootstrap percentile (perc, and bootstrap percentile (bca).

* Histogram including a dotted vertical line, which indicates the location of the original statistic.

* Quantile-quantile (q-q) plot, a graphical technique for determining if two data sets come from populations with a common distribution. The x-axis represents the standard normal distribution, while the y-axis denotes the distribution of the resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

# Load data for bootstrapping

boot.table <- data.frame(id = names(Idents(this_endo_obj)), cluster = Idents(this_endo_obj), 
                         sample = this_endo_obj$orig.ident)
rownames(boot.table) <- NULL

```

# Cell subtype percentages of Control 00d

## Bootstrap of the percentage of Homeostatic cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Homeostatic" & d2$sample == "00 d Control", ]) / 
	         nrow(d2[d2$sample == "00 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Differentiating cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Differentiating" & d2$sample == "00 d Control", ]) / 
	         nrow(d2[d2$sample == "00 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Perivascular macrophages cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Perivascular macrophages" & d2$sample == "00 d Control", ]) / 
	         nrow(d2[d2$sample == "00 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Neovascularizing cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Neovascularizing" & d2$sample == "00 d Control", ]) / 
	         nrow(d2[d2$sample == "00 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

# Cell subtype percentages of Control 07d

## Bootstrap of the percentage of Homeostatic cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Homeostatic" & d2$sample == "07 d Control", ]) / 
	         nrow(d2[d2$sample == "07 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Differentiating cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Differentiating" & d2$sample == "07 d Control", ]) / 
	         nrow(d2[d2$sample == "07 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Perivascular macrophages cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Perivascular macrophages" & d2$sample == "07 d Control", ]) / 
	         nrow(d2[d2$sample == "07 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Neovascularizing cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Neovascularizing" & d2$sample == "07 d Control", ]) / 
	         nrow(d2[d2$sample == "07 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

# Cell subtype percentages of Control 28d

## Bootstrap of the percentage of Homeostatic cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Homeostatic" & d2$sample == "28 d Control", ]) / 
	         nrow(d2[d2$sample == "28 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Differentiating cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Differentiating" & d2$sample == "28 d Control", ]) / 
	         nrow(d2[d2$sample == "28 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Perivascular macrophages cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Perivascular macrophages" & d2$sample == "28 d Control", ]) / 
	         nrow(d2[d2$sample == "28 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Neovascularizing cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Neovascularizing" & d2$sample == "28 d Control", ]) / 
	         nrow(d2[d2$sample == "28 d Control", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

# Cell subtype percentages of PLX5622 00d

## Bootstrap of the percentage of Homeostatic cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Homeostatic" & d2$sample == "00 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "00 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Differentiating cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Differentiating" & d2$sample == "00 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "00 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Perivascular macrophages cells

There is no Perivascular macrophages cells in this treatment condition.

```{r,echo=F,eval=F,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Perivascular macrophages" & d2$sample == "00 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "00 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}


# The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.
# 
# The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Neovascularizing cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Neovascularizing" & d2$sample == "00 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "00 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

# Cell subtype percentages of PLX5622 07d

## Bootstrap of the percentage of Homeostatic cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Homeostatic" & d2$sample == "07 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "07 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Differentiating cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Differentiating" & d2$sample == "07 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "07 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Perivascular macrophages cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Perivascular macrophages" & d2$sample == "07 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "07 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Neovascularizing cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Neovascularizing" & d2$sample == "07 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "07 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

# Cell subtype percentages of PLX5622 28d

## Bootstrap of the percentage of Homeostatic cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Homeostatic" & d2$sample == "28 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "28 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Differentiating cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Differentiating" & d2$sample == "28 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "28 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Perivascular macrophages cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Perivascular macrophages" & d2$sample == "28 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "28 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

## Bootstrap of the percentage of Neovascularizing cells

Summary of the bootstrap resamples:

```{r,echo=F,eval=T,message=FALSE,warning=F}

# library(boot)

# "Homeostatic", "Differentiating", "Perivascular macrophages", "Neovascularizing"

fc <- function(d, i){
	d2 <- d[i,]
	return(nrow(d2[d2$cluster == "Neovascularizing" & d2$sample == "28 d PLX5622", ]) / 
	         nrow(d2[d2$sample == "28 d PLX5622", ]))
}

set.seed(626)
bootcorr <- boot(boot.table, fc, R = 10000)

summary(bootcorr)

```

```{r,echo=F,eval=F,message=FALSE,warning=F}

var(bootcorr$t)

```

The variance of the percentage of homeostatic cells in the bootstrap resamples is `r var(bootcorr$t)`.

The confidence interval of the percentage of homeostatic cells in the bootstrap resamples.

```{r,echo=F,eval=T,message=FALSE,warning=F}

plot(bootcorr)
boot.ci(boot.out = bootcorr, type = c("norm", "basic", "perc", "bca"))

```

```{r, eval = T}

```



```{r, eval = T}

```


```{r, eval = T}

```


```{r, eval = T}

```


```{r, eval = T}

```


```{r, eval = T}

```


```{r, eval = T}

```
